Determining Most-Suitable Refactoring Techniques for Refactoring Code Clones

### 2019-11-29 cefp/paper.tex
Conclusion and new title

\begin{document}
%
\title{Mining Software Repositories for Contextual Information of Code Clones}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Simon Baars\inst{1,2}\orcidID{0000-0001-7905-1027} \and
Ana Oprescu\inst{1,3}\orcidID{0000-0001-6376-0750}}
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Amsterdam \and
\email{simon.j.baars@gmail.com} \and
\email{A.M.Oprescu@uva.nl}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

@@

@@

\section{Conclusion}

>>>>

\begin{document}
%
\title{Determining Most-Suitable Refactoring Techniques for Refactoring Code Clones}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Simon Baars\inst{1,2}\orcidID{0000-0001-7905-1027} \and
Ana Oprescu\inst{1,3}\orcidID{0000-0001-6376-0750}}
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Amsterdam \and
\email{simon.j.baars@gmail.com} \and
\email{A.M.Oprescu@uva.nl}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

@@

\section{Background}

@@

\section{Conclusion}
To determine which refactoring techniques are most suitable to refactor most clones, we analyzed their context. We measured the \textbf{relation} through inheritance of clone instances in a clone class. In our corpus, we found that 37\% of clones are found in the same class. 24\% of clones are in the same inheritance hierarchy. Another 24\% of clones are unrelated. The final 15\% of clones have the same interface. We also looked at the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.

From this, we conclude that the ``Extract Method'' refactoring technique is most suitable to refactor most clones.
